Kronos \& Krios: TBD

### 2017-05-23 paper/ms.tex
Add text on toy calculation and Li (wip)

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}

@@

Wide binaries are valuable tools for studying star and planet formation as well as
Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
\todo{Give specific examples.}
On the other hand, they are also a prime target to test the
chemical tagging hypotheses that we may trace back a group of co-eval stars
by detailed chemical abundance patterns as ``tag''s.
A multiple-star system of any size that we believe are co-eval,
with massive open clusters at one extreme, can serve this purpose.
Wide binaries are at the other extreme in that we may be less confident of
their coevality but they are much more abundant than the larger systems like open clusters.

@@

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
obtained high resolution spectroscopy for both \sunanalog\ and \bizarreone.
\todo{from where? mention briefly Keck HIRES}
The resulting measurements from this effort include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:t2}.

@@

% summarize other pair studies in detailed chemical abundance here

@@

estimate: 10 earth mass

@@

@@

We summarize the few wide separation common proper motion pairs that have been
studied in detailed chemical abundance so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
Main properties of the systems relevant to the present discussion are
summarized in \tablename~\ref{tab:otherstudies}.
Their reported abundance differences $\Delta\elemH{X}$ where the difference is
always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
comparision with this pair.

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (correspoding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$).
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.

>>>>

% packages
\definecolor{cbblue}{HTML}{3182bd}
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath,amssymb,natbib}
\usepackage[flushleft]{threeparttable}
\hypersetup{backref,breaklinks,colorlinks,urlcolor=cbblue,linkcolor=cbblue,citecolor=black}
\graphicspath{{figures/}}
\bibliographystyle{aasjournal.bst}

@@

Wide binaries are valuable tools for studying star and planet formation as well as
Galactic dynamics and chemical evolution.
In the context of studying the evolution of the Milky Way, they are useful for
two main reasons.
First, because wide binaries are weakly bound systems that may be tidally
disrupted by e.g., field stars, molecular clouds, or the Galactic tidal field,
their statistics can be informative of the Galactic mass distribution.
\todo{Give specific examples.}
On the other hand, they are also a prime target to test the
chemical tagging hypotheses that we may trace back a group of co-eval stars
by detailed chemical abundance patterns as ``tag''s.
A multiple-star system of any size that we believe are co-eval,
with massive open clusters at one extreme, can serve this purpose.
Wide binaries are at the other extreme in that we may be less confident of
the coevality of individual systems
but they are much more abundant than the larger systems like open clusters,
rendering their statistics a meaningful indication of whether the hypothesis works.

@@

In a separate effort to study detailed chemical abundances of
potential planet-hosting stars, \citet{2016ApJS..225...32B}
analyzed high resolution spectra of both stars obtained using HIRES spectrograph
on Keck~I telescope.
The spectral resolution is \todo{$R\approx XXX$} and the wavelength coverage is \todo{$XXX-XXX$~\AA}.
The resulting measurements include abundances measured for 15
chemical species (C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as
well as high precision radial velocities.
Other stellar parameters derived from these spectra are included in
\tablename~\ref{tab:t2}.

@@

@@

@@

One can carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere when adding material of e.g., bulk Earth composition
under these assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
\end{itemize}
We take the solar abundances $\elemH{X}$ of \citealt{Asplund:2009aa}
which can be converted to mass fraction in each element $X$ as in
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in e.g., atomic mass unit.
One can check that the \citealt{Asplund:2009aa} abundances
are consistent with mass fraction in \elem{H}, \elem{He} and metals
$X,\,Y,\,Z=0.757,\,0.249,\,0.0134$ as stated in that work.
Assuming a fraction of the star's convective zone in mass $f_\mathrm{CZ}$,
and that the added material has a total mass $M_\mathrm{add}$ and mass fraction in each
element $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star} + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
We take the composition of bulk Earth from a chondritic model of the Earth
(\citealt{mcdonough2001composition}) and CI chondrite from \citealt{2009LanB...4B...44L}.

Figure~\ref{fig:toycalc} shows the expected change of surface abundances in a
Sun-like star after $20~\mearth$ of material with composition of bulk Earth or
CI chondrite is added.
The CI chondrites are believed to have the closest in composition to the solar nebular.
Their composition closely matches that of the solar atmosphere except
Li, highly volatile ($\Tcondens < 250$~K) elements, and the noble gases.
Other groups of chondrites show differing level of variations from CI chondrites.
It has been long known that compared to CI or other carbonaceous chondrites,
the composition of the Earth shows a volatilaity trend that moderately volatile
elements (including Mn and Na) and volatile elements are incearsingly more
depleted with decreasing condensation temperature (\citealt{mcdonough2001composition}).
This trend is presumed to be closely related to the formation of terrestrial planets.
Given the simplistic assumptions laid out above, and the uncertainties
in our current knowledge of the compositions of terrestrial planets including bulk Earth,
the match between our toy calculation and the observed abundance difference
between \bizarreone\ and \sunanalog\ is remarkable.

% some discussion of individual elements

The element \elem{Li} is worth a special attention in the context of accretion scenario.
Because Li is present in either carbonaceous chondrites or the bulk Earth with
a concentration of $1-1.5$~ppm in mass (\citealt{mcdonough2001composition,}),
but is depleted over time on the surface of a Sun-like star, accretion of
either at later time will significantly replenish the lithium on the star's
surface.
For the present-day Sun, the accretion of $20~\mearth$ of bulk Earth-like
material results in $\Delta\elemH{Li} \approx 1.6$~dex.
Incidentally, the star under examination, \bizarreone, has an age (informed by
stellar parameters) very close to the Sun ().
Thus, as long as we believe the Sun's present-day surface Li abundance
to be ordinary, this predicts that the \bizarreone\ should have $1.6$~dex enhancement
in its Li.
This is in fact exactly what we find: the Li abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t2}, \todo{CITE JM?})
approximately $1.6$~dex higher than the solar value of $1.1$~dex.
Furthermore, this implies that the accretion event should have happened
very recently from a time ago that is shorter than the \elem{Li} depletion time.

It is further worth pointing out that measuring the \elem{Li} abundance
with some of the refractory elements such as $\elem{Fe}$
provides a way to estimate the time of the event.
%exlain

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{toycalc.pdf}
  \caption{Solar surface abundance change expected from adding $20~\mearth$ of
    material with bulk Earth or CI chondrite composition.
    The assumed mass fraction in the convective zone is $0.03$.
    For bulk earth composition, which is a closer match to the abundance difference
    seen in \bizarreone\ and \sunanalog, we indicate measured elements with black boundary
    lines around symbols.
  }
  \label{fig:toycalc}
\end{figure}

@@

We summarize the few wide separation common proper motion pairs that have been
studied in detailed chemical abundance so far.
These systems are HD~20782/HD~20781, HD~80606/HD~80607, XO-2N/XO-2S, HAT-P-1,
WASP-94A/WASP94-B, and HD~133131A/HD~133131B.
Main properties of the systems relevant to the present discussion are
summarized in \tablename~\ref{tab:otherstudies}.
Their reported abundance differences $\Delta\elemH{X}$ where the difference is
always taken as $\mathrm{higher}~\feh - \mathrm{lower}~\feh$ are plotted in
\figname~\ref{fig:relabun_tcrank} as a function of \Tcondens-rank for
comparison with this pair.

{\bf HD~20782/HD~20782:} 
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf stars (G2/G9.5)
with a projected separation of $\sim9000$~AU (corresponding to 4.2~arcmin sky separation).
Both stars in this system host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$) orbit with a
pericenter distance of 1.4~AU while HD~20781 hosts two Neptune-mass planets within 0.3~AU
with moderately high eccentricity ($e\sim0.1-0.3$).
They found that the abundances of 15 elements between the two stars are consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of $10-20$~\mearth\ of 
H-depleted rocky material that were pushed in during giant planet migration.
